Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Edit Trading Model
Modify related work

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\

@@

\section{Related Work}
The increasing IoT devices brings a huge amount of data, the economic value becomes essential for parties intended to sell, buy and find data. The need for IoT data marketplace arises due to this. Recent years, several researchers has started to explore based on this concept. There are some critical issues need to be resolved in the design of data marketplace platform, in this paper, we focus on two issues, data integrity and the trading behavior.

To ensure data integrity for IoT applications is always a challenge because of the unstandardize data format and dynamic nature. Moreover, the Third Party Auditors (TPAs)-based frameworks is far from being satisfactory. Therefore a decentralized data integrity validation has been proposed recent years, and blockchain is considered a solution.

Data Integrity as a Service (DIaas) is a blockchain based framework for data integrity proposed by Bin Liu\cite{DIaas}. DIaas is a Cloud Server Service (CSS) for IoT dynamic data that allows both data owner and data consumer to validate data integrity by comparing hashes on smart contract  and on Cloud Server. Besides, smart contract can also realize the purchase agreement, including authorizing data consumer for specific data set and even the penalty for data provider if they fail to provide the data integrity. However, the performance analysis shows that IoT devices still have low efficiency interacting with Etheruem, this may fall to the Proof-of-Work (PoW) process is time-consuming for an IoT device and the blockchain consensus can not be reached within a short time, while Ethereum is expected to enable consensus within 12-second but the time is still longer when the authors wrote the paper.

By solving the inefficiencies of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry or Web 3.0 based on the revolutionary distributed ledger technology, the \textbf{Tangle}. It is a secure, scalable and feeless transaction settlement layer which enables micropayments transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which adds functionality to emit and access an encrypted data stream over the Tangle where privacy and integrity meet is introduced to public. On the basis of the Tangle and MAM, IOTA foundation proposed a fully decentralized Data MarketPlace which is suitable for IoT streaming data that not only allow data owners and consumers to trade on Tangle but also protect privacy and assure data integrity from source with MAM. But only the data buyout doesn't meet the need of the real world, such as data subscription and a specific time period of data maybe needed for different uses. Moreover, even though IOTA needs less computing power than other blockchain system, doing PoW and unstable network environment are still the bottleneck for low-level devices, it may take 2 or more minutes to issue a transaction to Tangle under MAM protocol.

A different framework design proposed by Pooja Gupta, Salil S.Kanhere and Raja Jurdak\cite{3tierDataMarket} could solve the efficiency problem as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with smart contract which consists of provider, consumer and broker. Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers. However, there are some potential threats need to be resolved, such as payment fairness, authentication of the participants, faithful delivery of data and probable malicious behaviour of data marketplace participants.

@@

Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture that put data stream and trading process on distrubted ledgers. In our infrastructure, the identity of each participants could be easily verified with a self-soverign identity system, also we design the refunding mechanism to protect the payment fairness. Moreover, with MAM as our data storage on IOTA, data could be delivered securely and faithfully without any third-parties.

\section{System Architecture}
\subsection{Participants}
There are four major roles in the decentralized data marketplace (Figure \ref{fig:system_design}).

@@

\subsection{Game Theory Evaluation}

Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $P_s$, in total to buy the data.

@@

\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discount factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{itemize}
\item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
\item  More than 51\% of data buyers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out if wrong data or low accuracy data are delivered to data buyers.
\end{itemize}

Based on the description above, the discount sum of payoff for our repeated game is 
\begin{equation} \label{payoff}
\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

>>>>

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering National Taiwan University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

@@

\section{Related Work}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract and Cloud Server. Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization. However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers. Also, the performance analysis shows that IoT devices have low efficiency interacting with Etheruem due to the time-consuming Proof-of-Work(PoW) process.

By solving the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, a second layer data communication protocol which allows to emit and access an encrypted data stream over the Tangle where privacy and integrity meet.

On the basis of the Tangle and MAM, IOTA foundation proposed a decentralized Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from IOTA team to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker. Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant are still future work.

@@

The previous work proposed different solution to specific issues of data marketplace. In this paper, we proposed an  overall design of decentralized data markeplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.

\section{System Architecture}
Our proposed data marketplace framework is a 3-tier decentralized and trustless architecture with a registrar who is responsible for marketplace registration in order to put participants' information on distributed ledgers for validation, brokers who interact between data providers and consumers, including data uploading, product metadata generation and trading process, data providers who upload data, and data consumers who search for interested products and issue a new trade.

\subsection{Participants}
There are four major roles in the decentralized data marketplace (Figure \ref{fig:system_design}).

@@

\subsection{Game Theory Evaluation}
\subsubsection{Repeated Game}
Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

\subsubsection{Model Description}
We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay subscription fee, $p_s$, each person. The sum of all the subscription fee pays to data provider is denoted as $P_s$.

@@

\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discounted factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{itemize}
\item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
\item  More than 51\% of data buyers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
\item  One of the data buyers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to data buyers, this examiner will spread this information out.
\end{itemize}

Based on the description above, the discounted sum of payoff for our repeated game is 
\begin{equation} \label{payoff}
\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}
